Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-04-16 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Entering the size and power

# author citation list in chicago format
authorcitation: |
  Frery, A.C.; Alpala, J.; Nascimento,A.D.C.
# firstnote to eighthnote
#firstnote: |
 # Current address: Updated affiliation
#secondnote: |
  #These authors contributed equally to this work.
correspondence: |
  alejandro.frery@vuw.ac.nz
# document options
journal: remotesensing
type: article
status: submit
# front matter
#simplesummary: |
  #A Simple summary goes here.
abstract: |
  This paper presents a statistical approach to identify the underlying roughness characteristics in synthetic aperture radar (SAR) intensity data. 
  The physical modeling of this kind of data allows to use the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell, and none dominates the return. This situation is often called "homogeneous" or  "textureless" regions. 
  The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions, i.e., areas in which the fully-developed speckle hypotheses do not hold. 
  We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e. between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks. 
  The first test statistic uses a bootstrapped nonparametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
  The second test uses the classical coefficient of variation. 
  The third test uses an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median. 
  We apply our test statistic to create maps of \(p\) values for the homogeneity hypothesis.
  These maps identify different types of targets. 
  We show that our proposal outperforms its competitors using simulated and SAR data.
# ACF Which is "our proposal" and which are the "competitors"?
keywords: |
  SAR; heterogeneity; entropy;  coefficient of variation; hypothesis tests
acknowledgement: |
  This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior - Brasil (CAPES) - Finance Code 001.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
funding: |
  Please add: "This research received no external funding" or "This research 
  was funded by NAME OF FUNDER grant number XXX."  and ``The APC was funded 
  by XXX''. Check carefully that the details given are accurate and use the 
  standard spelling of funding agency names at 
  \url{https://search.crossref.org/funding}, any errors may affect your future 
  funding.
institutionalreview: |
 Not applicable.
#informedconsent: |
  # Any research article describing a study involving humans should contain this 
  # statement. Please add ``Informed consent was obtained from all subjects 
  # involved in the study.'' OR ``Patient consent was waived due to REASON 
  # (please provide a detailed justification).'' OR ``Not applicable'' for 
  # studies not involving humans. You might also choose to exclude this statement 
  # if the study did not involve humans.

@@

The coefficient of variation (CV), introduced in 1896 by Pearson&nbsp;\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields&nbsp;\cite{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
It facilitates the comparison of variability between different populations and is particularly valuable for comparing variables with different units. 
This is because when the main purpose is to compare the variations of several variables, the standard deviation can only serve as an adequate measure of variation if all variables are expressed in the same unit of measurement and have identical means. 
If these conditions are not met for the variables under investigation, the CV is the relative measure that is usually used in real applications. The variable with the highest CV value is the one with the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.

In our study, entropy serves as a fundamental parameter that allows a robust evaluation using a bootstrapped nonparametric estimator of the Shannon entropy.
At the same time, we use the classical CV and an alternative form based on the ratio between the median absolute deviation and the median. 
The CV is known as an efficient and robust index for texture information and measures the homogeneity of the image&nbsp;\cite{Lopes1990}.
Applying these test statistics to generate maps of \(p\) values facilitates testing the homogeneity hypothesis and reveals different types of targets in the SAR data. 
Through extensive experiments with real and simulated SAR data, we demonstrate the superiority of our proposed method over existing approaches.

Applying these test statistics to generate $p$-value maps facilitates testing of the homogeneity hypothesis, revealing diverse types of targets within the SAR data. 
Through extensive experimentation involving real and simulated SAR data, we demonstrate the superiority of our proposed methodology over existing approaches.

The article is structured as follows: Section&nbsp;\ref{sec:Background}
deals with statistical modeling and entropy estimation for intensity SAR
data. 
Section&nbsp;\ref{sec:test} outlines hypothesis tests based on nonparametric entropy estimators and coefficients of variation. 
In Section&nbsp;\ref{sec:Results} we present experimental results. 
Finally, in Section&nbsp;\ref{sec:conclusion} the conclusions are presented.

@@

If we take the law with the density&nbsp;\eqref{E:gi01}, the \(r\)th non-central moment of \(Z\) is expressed as follows:
\begin{align}
    E_{G_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, \quad \alpha <-r. 
    \label{E:rmom}
\end{align}

Although the \(\mathcal{G}_I^0\) distribution is defined by the parameters \(\alpha\) and \(\gamma\), in the SAR literature&nbsp;\cite{Nascimento2010} the texture \(\alpha\) and the mean \(\mu\) are usually used. In this way, we calculate the expected value \(\mu\) using the expression in&nbsp;\eqref{E:rmom}, and we reparametrize&nbsp;\eqref{E:gi01} with \(\mu\),
\(\alpha\), and \(L\).
Then \begin{align*}
    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
\end{align*} 
The reparametrized pdf that characterizes the law \(G_I^0(\mu, \alpha, L)\) is thus
\begin{equation}
        f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}.\label{E:gi02}
\end{equation}

@@

Using&nbsp;\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$in&nbsp;\eqref{E:gamma1} and $G_I^0$ in&nbsp;\eqref{E:gi02} based on&nbsp;\cite{Cassetti2022} and&nbsp;\cite{Ferreira2020}:
\begin{equation}
\label{E:E-gamma}
H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
\end{equation}
\begin{multline}
\label{E:E-GIO}
H_{G_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu -\ln\Gamma(L-\alpha)\\
+ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L,
\end{multline}
where $\psi^{(0)}(\cdot)$ is the digamma function. Figure&nbsp;\ref{fig:Plot_GI0_to_gamma1}, shows the behavior of the entropy of \(G_I^0\) when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), where the approximation to the entropy of \(\Gamma_{\text{SAR}}\) can be observed when \(\alpha\) assumes large negative values.
In an interpretative sense, we can conclude that the more heterogeneous (high values of $\alpha$) the SAR region is, the higher the value of entropy (or degree of disorder).
It is worth noting that this conclusion confirms what is written in the SAR literature.

@@

The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including&nbsp;\cite{vasicek1976test, Wieczorkowski1999,correa1995new,AlOmari2019}, who have proposed estimators based on spacings.

One of the first non-parametric estimators based on spacings was introduced by Vasicek&nbsp;\cite{vasicek1976test}. 
Under the assumption that \(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) is a random sample from the distribution \(F(z)\), the estimator is defined as:
\begin{equation*}
\label{E:Vas}
	\widehat{H}_{\text{V}}(\bm{Z})=\frac{1}{n}\sum_{i=1}^{n}\ln\left[\frac{n}{2m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
	\end{equation*}
where $m<n/2$ is a positive integer, $Z_{(i+m)}-Z_{(i-m)}$ is the $m$-spacing and $Z_{(1)}\leq Z_{(2)}\leq\ldots\leq Z_{(n)}$ are the order statistics and $Z_{(i)}= Z_{(1)}$ if $i<1$, $Z_{(i)}= Z_{(n)}$ if $i>n$.

Several authors have explored adaptations to Vasicek's estimator. 
We consider three estimators known for their superior performance&nbsp;\cite{Cassetti2022}:
Correa&nbsp;\cite{correa1995new}, \(\widehat{H}_{\text{C}}\);
Ebrahimi et al&nbsp;\cite{Ebrahimi1994}, \(\widehat{H}_{\mathrm{E}}\);
and Al Omary&nbsp;\cite{IbrahimAlOmari2014}, \(\widehat{H}_{\mathrm{AO}}\).

## Enhanced Bootstrap Technique

We use the bootstrap technique to refine the accuracy of existing nonparametric entropy estimators. In this approach, new data sets are generated by replicate sampling from an existing data set&nbsp;\cite{Michelucci2021}.

Let us assume that non-parametric entropy estimators
\(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, i.e:\begin{equation}
\label{Eq:bias1}
\operatorname{Bias}\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
\end{equation} Our bootstrap-improved estimators are of the form:
\begin{align*}
\widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
\end{align*} 
where \(B\) is the number of replications in the bootstrap
technique. 
Applying this methodology, the original estimators of Correa,
Ebrahimi and Al-Omari are now referred to as the proposed bootstrap-enhanced versions:
\(\widetilde{H}_{\text{C}}\),
\(\widetilde{H}_{\text{E}}\), and \(\widetilde{H}_{\text{AO}}\),
respectively.

We analyzed the performance of these estimators with a Monte Carlo study: \(500\) samples of \(G_I^0\) of size
\(n\in\left\{9, 25, 49, 81, 121\right\}\) and different values for mean, number of looks and roughness. We present the results with
\(\mu\in\left\{1, 10\right\}\), \(\alpha=-10\) and \(L=5\). The results are also adherent for the other situations. In the bootstrap technique, each sample is replicated a hundred times with replacement. We use the following heuristic formula for spacing,
\(m=\left[\sqrt{n}+0.5\right]\).

In Figure&nbsp;\ref{fig:Plot_bias_mse_gi0} we show comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions. The use of the bootstrap technique shows higher precision, lower bias and MSE, and improved convergence. The results of the simulation can be found in
Table&nbsp;\ref{tab:table2}.

The precision of the estimators resulting from the comparison of bias and MSE benefits significantly from the bootstrap technique, especially for sample sizes below 81.

@@

We explore a robust alternative to CV, as described in&nbsp;\cite{Ospina2019}, which incorporates the ratio between the mean absolute deviation from the median (MnAD) and the median, two well-known robust measures of
scale and location, respectively. The sample version for the MnAD is defined as
\(n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|\), where \(\widehat{Q}_2\)
is an estimate for the median of the population, which can be approximated by the median of the sample.

@@

We aim at testing the following hypotheses:

$$
 \begin{cases}\mathcal{H}_0: \text{ The data comes from the } \Gamma_{\text{SAR}}\\ 
  \mathcal{H}_1:\text{ The data comes from the } G_I^0.\end{cases}
$$
In the physical sense, we are testing the hypothesis that the data are fully-developed speckle.
As for the parametric problem, once it is not possible to define the hypothesis $\mathcal{H}_0=\alpha=-\infty$, it is impossible to solve this problem with the parametric statistical inference alternatives (such as likelihood ratio, score, grandient and Wald hypothesis test).
The proposed tests to solve this physical problem in SAR systems are described below.

@@

The first test statistic evaluates the behavior of the data under the null hypothesis using the empirical distribution: 
\begin{equation}
\label{Eq:test_e}
S_H= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{Z}\right].
\end{equation}
The values should be around zero under the null hypothesis and far otherwise. 
<!-- This suggests significant differences and implies the presence of heterogeneous clutter. -->
Figure&nbsp;\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, SD, variance (Var), skewness (SK), excessive kurtosis (EK) and Anderson--Darling \(p\) values for normality. 
Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption. A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, symmetry and a slight tail.
Normal QQ plots confirm that there is no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.

@@

After checking the normality of the data, we examined the possibilities of the proposed test in terms of size and power.
Under \(\mathcal{H}_0\), the distribution of the test statistic is asymptotically normal.
Therefore, the \(p\) value is calculated as
\(2\Phi(-\mid \varepsilon\mid)\), where \(\Phi\) is the standard
Gaussian cumulative distribution and \(\varepsilon\) is the standardized test statistic given by :
\[
\varepsilon=\frac{\widetilde{H}-H_{\Gamma_{\text{SAR}}}}{\hat\sigma}.
\]

@@

## Real Data

>>>>

# author citation list in chicago format
authorcitation: |
  Frery, A.C.; Alpala, J.; Nascimento,A.D.C.
# firstnote to eighthnote
#firstnote: |
 # Current address: Updated affiliation
#secondnote: |
  #These authors contributed equally to this work.
correspondence: |
  alejandro.frery@vuw.ac.nz
# document options
journal: remotesensing
type: article
status: submit
# front matter
#simplesummary: |
  #A Simple summary goes here.
abstract: |
  This paper presents a statistical approach to identify the underlying roughness characteristics in synthetic aperture radar (SAR) intensity data. 
  The physical modeling of this kind of data allows to use the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell, and none dominates the return. This situation is often called "homogeneous" or  "textureless" regions. 
  The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions, i.e., areas in which the fully-developed speckle hypotheses do not hold. 
  We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e. between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks. 
  The first test statistic uses a bootstrapped non-parametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
  The second test uses the classical coefficient of variation. 
  The third test uses an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median. 
  We apply our test statistic to create maps of \(p\) values for the homogeneity hypothesis.
  These maps identify different types of targets. 
  We show that our proposal outperforms its competitors using simulated and SAR data.
# ACF Which is "our proposal" and which are the "competitors"?
keywords: |
  SAR; heterogeneity; entropy;  coefficient of variation; hypothesis tests
acknowledgement: |
  This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior - Brasil (CAPES) - Finance Code 001.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
funding: |
  Please add: "This research received no external funding" or "This research 
  was funded by NAME OF FUNDER grant number XXX."  and ``The APC was funded 
  by XXX''. Check carefully that the details given are accurate and use the 
  standard spelling of funding agency names at 
  \url{https://search.crossref.org/funding}, any errors may affect your future 
  funding.
institutionalreview: |
 Not applicable.
#informedconsent: |
  # Any research article describing a study involving humans should contain this 
  # statement. Please add ``Informed consent was obtained from all subjects 
  # involved in the study.'' OR ``Patient consent was waived due to REASON 
  # (please provide a detailed justification).'' OR ``Not applicable'' for 
  # studies not involving humans. You might also choose to exclude this statement 
  # if the study did not involve humans.

@@

The coefficient of variation (CV), introduced in 1896 by Pearson&nbsp;\cite{Pearson1896}, is a relative dispersion measure widely used in various fields of applied statistics, including sampling, biostatistics, medical and biological research, climatology and other fields&nbsp;\cite{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
It facilitates the comparison of variability between different populations and is particularly valuable for comparing variables with different units. 
This is because when the main purpose is to compare the variations of several variables, the standard deviation can only serve as an adequate measure of variation if all variables are expressed in the same unit of measurement and have identical means. 
If these conditions are not met for the variables under investigation, the CV is the relative measure that is usually used in real applications. The variable with the highest CV value is the one with the largest relative dispersion around the mean value&nbsp;\cite{Banik2011}.
The coefficient of variation is the basic measure of heterogeneity in SAR data&nbsp;\cite{oliverquegan98}.
We study two ways of estimating the coefficient of variation.

The other parameter we study is the Shannon entropy.
Different models for SAR data have different entropy values, but this fundamental quantity can be also estimated in a model-agnostic way.
We exploit this property and design a bootstrap-improved non-parametric estimator for the Shannon entropy.

We devise test statistics based on these three estimators: the classical coefficient of variation, a robust version, and the Shannon entropy estimator.
We apply these test statistics to generate maps of evidence of homogeneity
that reveal different types of targets in the SAR data. 
Through extensive experiments with simulated and SAR data, we demonstrate the superiority of our proposed method over existing approaches.

The article is structured as follows: Section&nbsp;\ref{sec:Background}
deals with statistical modeling and entropy estimation for intensity SAR
data. 
Section&nbsp;\ref{sec:test} outlines hypothesis tests based on non-parametric entropy and coefficients of variation estimators. 
In Section&nbsp;\ref{sec:Results} we present experimental results. 
Finally, we draw our conclusions in Section&nbsp;\ref{sec:conclusion}.

@@

If we take the law with the density&nbsp;\eqref{E:gi01}, the \(r\)th non-central moment of \(Z\) is expressed as follows:
\begin{align}
    E_{\mathcal{G}_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, \quad \alpha <-r. 
    \label{E:rmom}
\end{align}

Although the \(\mathcal{G}_I^0\) distribution is defined by the parameters \(\alpha\) and \(\gamma\), in the SAR literature&nbsp;\cite{Nascimento2010} the texture \(\alpha\) and the mean \(\mu\) are usually used. 
The expected value \(\mu\) using the expression in&nbsp;\eqref{E:rmom} is
\begin{equation}
    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1},
\end{equation} 
and we reparametrize&nbsp;\eqref{E:gi01} with \(\mu\) obtaining:
\begin{equation}
        f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}.\label{E:gi02}
\end{equation}

@@

Using&nbsp;\eqref{E:entropy2}, we obtain the Shannon entropy of $\Gamma_{\text{SAR}}$ in&nbsp;\eqref{E:gamma1} and $G_I^0$ in&nbsp;\eqref{E:gi02}:
\begin{equation}
\label{E:E-gamma}
H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
\end{equation}
\begin{multline}
\label{E:E-GIO}
H_{G_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu -\ln\Gamma(L-\alpha)\\
+ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L,
\end{multline}
where $\psi^{(0)}(\cdot)$ is the digamma function. Figure&nbsp;\ref{fig:Plot_GI0_to_gamma1}, shows the entropy of \(G_I^0\) as a function of $\mu$ when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\).
Notice that it converges to the entropy of \(\Gamma_{\text{SAR}}\) when \(\alpha\to-\infty\), as expected.
The more heterogeneous (large $\alpha$ values) the SAR region is, the larger the entropy (or degree of disorder) is.

@@

Several authors&nbsp;\cite{vasicek1976test, Wieczorkowski1999,correa1995new,AlOmari2019} have studied the problem of the non-parametric estimation of $H(Z)$.
Their proposals use estimators based on differences between order statistics: spacings.

One of the first non-parametric estimators based on spacings was introduced by Vasicek&nbsp;\cite{vasicek1976test}. 
Under the assumption that \(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) is a random sample from the distribution \(F(z)\), the estimator is defined as:
\begin{equation*}
\label{E:Vas}
	\widehat{H}_{\text{V}}(\bm{Z})=\frac{1}{n}\sum_{i=1}^{n}\ln\left[\frac{n}{2m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
	\end{equation*}
where $m<n/2$ is a positive integer, $Z_{(i+m)}-Z_{(i-m)}$ is the $m$-spacing and $Z_{(1)}\leq Z_{(2)}\leq\ldots\leq Z_{(n)}$ are the order statistics, $Z_{(i)}= Z_{(1)}$ if $i<1$, $Z_{(i)}= Z_{(n)}$ if $i>n$.

Several authors have explored adaptations to Vasicek's estimator. 
We consider three estimators known for their superior performance&nbsp;\cite{Cassetti2022}:
Correa&nbsp;\cite{correa1995new}, \(\widehat{H}_{\text{C}}\);
Ebrahimi et al&nbsp;\cite{Ebrahimi1994}, \(\widehat{H}_{\mathrm{E}}\);
and Al Omary&nbsp;\cite{IbrahimAlOmari2014}, \(\widehat{H}_{\mathrm{AO}}\).
<!-- ACF Define the estimators and state their main properties -->

These estimators are asymptotically consistent, 
but we will use improved bootstrap-improved versions because we need them to perform well with small samples.

## Enhanced estimators with Bootstrap

We use the bootstrap technique to refine the accuracy of non-parametric entropy estimators. 
In this approach, new data sets are generated by replicate sampling from an existing data set&nbsp;\cite{Michelucci2021}.

Let us assume that non-parametric entropy estimators
\(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, i.e:\begin{equation}
\label{Eq:bias1}
\operatorname{Bias}\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
\end{equation} Our bootstrap-improved estimators are of the form:
\begin{align*}
\widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
\end{align*} 
where \(B\) is the number of observations obtained by resampling from $\bm Z$ with replacement. 
Applying this methodology, the original estimators of Correa,
Ebrahimi and Al-Omari are now referred to as the proposed bootstrap-enhanced versions:
\(\widetilde{H}_{\text{C}}\),
\(\widetilde{H}_{\text{E}}\), and \(\widetilde{H}_{\text{AO}}\),
respectively.

We analyzed the performance of these estimators with a Monte Carlo study: \(500\) samples from the \(G_I^0\) law of size
\(n\in\left\{9, 25, 49, 81, 121\right\}\) and different mean, number of looks and roughness. 
We present the results with
\(\mu\in\left\{1, 10\right\}\), \(\alpha=-10\) and \(L=5\). 
The results are consistent with the other situations. 
We used $B=100$ bootstrap samples and the heuristic spacing
\(m=\left[\sqrt{n}+0.5\right]\), as recommended in the literature.

In Figure&nbsp;\ref{fig:Plot_bias_mse_gi0} we show the bias and mean squared error (MSE) of the original non-parametric entropy estimators and their respective bootstrap-enhanced versions. 
Bootstrap-enhanced estimators have smaller bias and MSE, especially for sample sizes below $81$.
The results of the simulation can be found in
Table&nbsp;\ref{tab:table2}.

@@

We explore a robust alternative to CV, as described by \citet{Ospina2019}, which incorporates the ratio between the mean absolute deviation from the median (MnAD) and the median, two well-known robust measures of
scale and location, respectively. The sample version for the MnAD is defined as
\(n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|\), where \(\widehat{Q}_2\)
is an estimate for the median of the population, which can be approximated by the median of the sample.

@@

We aim at testing the following hypotheses: 
$$
\begin{cases}
  \mathcal{H}_0: \text{ The data come from the } \Gamma_{\text{SAR}}\text{ law},\\ 
  \mathcal{H}_1:\text{ The data come from the } G_I^0 \text{ distribution}.
\end{cases}
$$
We are testing the hypothesis that the data are fully-developed speckle versus the alternative of data with roughness.
As for the parametric problem, once it is not possible to define the hypothesis $\mathcal{H}_0=\alpha=-\infty$, it is impossible to solve this problem with parametric  inference alternatives (such as likelihood ratio, score, gradient and Wald hypothesis test).
The proposed tests to solve this physical problem in SAR systems are described below.

@@

The first test statistic evaluates the behavior of the data under the null hypothesis using the empirical distribution: 
\begin{equation}
\label{Eq:test_e}
S_H= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{Z}\right].
\end{equation}
The values should be around zero under the null hypothesis and far otherwise. 
<!-- This suggests significant differences and implies the presence of heterogeneous clutter. -->
Figure&nbsp;\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, SD, variance (Var), skewness (SK), excessive kurtosis (EK) and Anderson--Darling \(p\) values for normality. 
Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption. A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, symmetry and a light tail.
Normal QQ plots confirm that there is no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.

@@

After checking the normality of the test statistics, we examined the possibilities of the proposed test in terms of size and power.
Under \(\mathcal{H}_0\), the distribution of the test statistic is asymptotically normal.
Therefore, the \(p\) value is calculated as
\(2\Phi(-|\varepsilon|)\), where \(\Phi\) is the standard
Gaussian cumulative distribution function, and \(\varepsilon\) is the standardized test statistic given by :
\[
\varepsilon=\frac{\widetilde{H}-H_{\Gamma_{\text{SAR}}}}{\hat\sigma}.
\]

@@

## SAR Data
